Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-29 manuscript.Rmd
internal consistency

df <- 
df %>% 
  mutate(
    across(all_of(negative_keyed_items), subtract_8)
  )

@@

table1 <-
tibble(
  var = names(descriptive_df),
  mean = map_dbl(descriptive_df, mean, na.rm = TRUE),
  sd = map_dbl(descriptive_df, sd, na.rm = TRUE)
)
```

>>>>

df <- 
df %>% 
  mutate(
    across(all_of(negative_keyed_items), subtract_8)
  )
```

@@

table1 <-
tibble(
  var = names(descriptive_df),
  mean = map_dbl(descriptive_df, mean, na.rm = TRUE),
  sd = map_dbl(descriptive_df, sd, na.rm = TRUE)
)

# internal consistency
source("items_reliability.R")

df_desc <- df %>% 
  distinct(perceiver_id)

map2_dfr(item_list, variable_names, ~ 
           get_reliability(df = df_desc, 
                           vars = .x, 
                           var_names = .y)
         )

df %>% 
  select(rse1:rse10rc) %>% 
  names()
```
